A universal standard archive file for adsorption data

### 2020-11-26 manuscript/article.tex
intro drafted

Measuring the interaction of gas with porous materials is crucial to understanding and comparing the plethora of different materials.
The quantity of gas adsorbed is measured in any convenient units, but for the presentation of the data, it is recommended that the amount adsorbed should be expressed in moles per gram of outgassed adsorbent. If possible, the composition of the adsorbent should be specified and its surface characterised. To facilitate the comparison of adsorption data, it is recommended that adsorption isotherms are displayed in a graphica form with the amount adsorbed (preferably presented using mol$\,$g$^-1$) plotted against the equilibrium relative pressure ($p/p_0$), where $p_0$ is the saturation pressure of the pure adsorptive at the operational temperature, or against absolute pressure, when the temperature is above the critical temperature of the adsorptive. If the adsorption measurements are made under conditions where the gas phase deviates appreciably from ideality (e.g., at high pressure), it is desirable that the isotherms should be presented in terms of gas fugacity rather than pressure.

Rapid advances in computer technology, coupled with the expansion of local, national and international networks, have fuelled the need for such a facility. The variety and relative inflexibility of existing data exchange formats have inhibited their ef- fective use. This is true even in fields where the basic data requirements are well defined. Problems of data ex- changearefurtherexacerbatedif thenumberandnatureof data types change rapidly and continuously. Under these conditions specialized and local file formats have prolif- erated. This diversity was tolerable when electronic data transfer was infrequent, or when data processing speeds required file formats finely tuned to specific applications. The developments cited above signal an end to this ration- ale. A general, flexible, rapidly extensible and universal file format protocol is now essential.It must be machine- independent and portable so that accessibility to data items is independent of their point of origin. It must allow new data items to be incorporated without the need to modify existing files.
Since the development of the first porous materials, there has been a sharp rise in the design of highly ordered and structured porous materials (Fig. S1). The advent of materials with more complex pore networks and dynamic frameworks through materials design strategies such as reticular chemistry has given rise to reported BET areas in excess of 8,000 m2 g1.[11,2528] Often, these complex materials have complex adsorption isotherms which have become harder to fit into the BET model. In response to these advances, materials scientists have developed a new generation of porosimetry equipment with pressure transducers capable of the collection of high-resolution gas adsorption isotherms at ultra-low pressures (<10-5 mmHg). Despite these advances, scientists still rely on the manual calculation of surface areas using BET theory

>>>>

Measuring the interaction of gas with a material is crucial to understanding and comparing the plethora of different porous materials.
The quantity of gas adsorbed is measured in any convenient units, but for the presentation of the data, the International Union of Pure and Applied Chemistry (IUPAC) has recommended that the amount adsorbed should be expressed in moles per gram of outgassed adsorbent.\cite{} Moreover, if possible, the composition of the adsorbent should be specified and its surface characterized. To facilitate the comparison of adsorption data, it is recommended that adsorption isotherms are displayed in a graphical form with the amount adsorbed (preferably presented using mol$\,$g$^-1$) plotted against the equilibrium relative pressure ($p/p_0$), where $p_0$ is the saturation pressure of the pure adsorptive at the operational temperature, or against absolute pressure, when the temperature is above the critical temperature of the adsorptive. If the adsorption measurements are made under conditions where the gas phase deviates appreciably from ideality (e.g., at high pressure), it is desirable that the isotherms should be presented in terms of gas fugacity rather than pressure.

Rapid advances in computer simulations, coupled with the expansion of fruitful local, national and international networks, have fueled the need for a standardization of adsorption data.
The variety and relative inflexibility of existing adsorption data formats can inhibit the effective use of reported data.
A general, flexible, rapidly extensible and universal file format protocol is essential to further accelerate the developed of porous materials.
As with other standard formats, this must be machine-independent and portable so that accessibility to data items is independent of their point of origin.
It must allow new data items to be incorporated without the need to modify existing files.
